Expression QTL hotspot dissection with mediation analysis and pleiotropy testing

### 2019-07-29 analysis/paper/hotspots-paper-Chr2-only.Rmd
increased travis_wait to 100

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
output: 
  bookdown::html_document2:
    pandoc_args: 
      - --filter
      - /usr/local/Cellar/pandoc-crossref/0.3.4.1/bin/pandoc-crossref
---

@@

$$
Y = \alpha 1 + WC + E
\label{model1}
$$

>>>>

---
title: "Expression QTL hotspot dissection with mediation analysis and pleiotropy testing"
author: "Frederick J. Boehm, Brian S. Yandell, and Karl W. Broman"
date: "7/27/2019"
bibliography: research.bib
numberSections: true
output: 
  bookdown::html_document2:
    pandoc_args: 
      - --filter
      - /usr/local/Cellar/pandoc-crossref/0.3.4.1/bin/pandoc-crossref
---

@@

$$
Y = \alpha 1 + WC + E
$$
